%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Author:
% Claud D. Park <posquit0.bj@gmail.com>
% http://www.posquit0.com
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Configuration
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Themes: Awesome-CV
\documentclass[12pt, a4paper]{awesome-cv}

%%% Override a directory location for fonts(default: 'fonts/')
\fontdir[fonts/]

%%% Configure a directory location for sections
\newcommand*{\sectiondir}{resume/}

%%% Override color
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight
%% Color for highlight
% Define your custom color if you don't like awesome colors
\colorlet{awesome}{awesome-red}
%\definecolor{awesome}{HTML}{CA63A8}
%% Colors for text
%\definecolor{darktext}{HTML}{414141}
%\definecolor{text}{HTML}{414141}
%\definecolor{graytext}{HTML}{414141}
%\definecolor{lighttext}{HTML}{414141}

%%% Override a separator for social informations in header(default: ' | ')
%\headersocialsep[\quad\textbar\quad]

\newif\ifelectronic
\electronicfalse

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     3rd party packages
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Needed to divide into several files
\usepackage{import}
\usepackage[super]{nth}
\usepackage{booktabs}
\newcommand{\tabitem}{~~\llap{\textbullet}~~}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Personal Data
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Essentials
\name{T.M. Harry}{Hsu}
\address{Tzu-Ming Harry Hsu, Department of Electrical Engineering and Computer Science, Massachusetts Institute of Technology}
\mobile{(+1) 617-803-7785} 
%%% Social
\email{stmharry@mit.edu}
\homepage{stmharry.github.io}
\github{stmharry}
%%% Optionals


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Content
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Make a footer for CV with three arguments(<left>, <center>, <right>)
\makecvfooter
{}
{Tzu-Ming Harry Hsu}
{\thepage}

\begin{document}
%%% Make a header for CV with personal data
\makecvheader

\iffalse
\cvsection{Upcoming Research}
\begin{cvskills}{2.5cm}{13.9cm}
    \cvskill{Signal Kinetics}
    {
        Signals are everywhere in our daily lives, and some of them is visible while others cannot be seen. Ranging from WiFi signals to brain waves, the pervasiveness of these signals results in networking the whole world through both natural and man-made links. The aim of my upcoming researches is to explore ways to link the natural and man-made links such that not only computers but humans can extend their abilities in communicating, sensing, and actuation. Tools from multiple fields are applied in order to extract the information of physical world and to explicitly relate them. }
    \cvskill{}
    {
        Computer networks aids us in sensing the status of a remote target, a patient, for example. We are able to collect the reflected signal from the subject's body, and then translate the signal into interpretable features with signal processing algorithms. The algorithms have to be carefully tailored to filter out unwanted influences of the outside world, which could be millions of times stronger than the desired signal. Having obtained the features, we thus apply machine learning techniques to learn and predict the subject's attributes such as health status, gesture, or even mood.
    }
    \cvskill{}
    {
        In my upcoming research starting September 2017, the aforementioned techniques will be applied to further strengthen the connection between humans and machines via interactions through signals. 
    }
\end{cvskills}
\fi

\cvsection{Research Interests}
\begin{cvskills}{0.7cm}{15.7cm}
    \cvskill{1}{Deep Learning}
    \cvskill{2}{Computer Vision}
    \cvskill{3}{Machine Learning}
\end{cvskills}

\cvsection{Skills}
\begin{cvskills}{2.2cm}{14.2cm}
    \cvskill{Programming}{Python (TensorFlow), C / C++, MATLAB, Caffe, Java, HTML / CSS / JS}
    \cvskill{Languages}{Mandarin Chinese (Native), Taiwanese (Native), English (Fluent), Spanish (Intermediate)}
    \iffalse
        \cvskill{GRE}{Verbal (153 / 170), Quantitative (170 / 170), Analytical Writing (4.0 / 6.0)}
        \cvskill{TOEFL iBT}{Reading (29 / 30), Listening (30 / 30), Speaking (22 / 30), Writing (27 / 30)}
    \fi
\end{cvskills}

\cvsection{Education}
\begin{cventries}
    \cventry
    {Ph.D. Student in Computer Science}
    {Massachusetts Institute of Technology (MIT)}
    {Cambridge, MA, USA}
    {Sep. 2017 - Now}
    {}

    \cventry
    {B.S.E. in Electrical Engineering and B.S. in Physics}
    {National Taiwan University (NTU)}
    {Taipei, Taiwan}
    {Sep. 2011 - Jun. 2016}
    {
        \vspace{-3mm}
        \begin{cvskills}{2.7cm}{13.7cm}
            \cvskill{GPA}{Overall (3.99 / 4.00), Last 60 units (3.99 / 4.00)}
            \cvskill{Overall ranking}{1 / 190}
            \cvskill{Relevant courses}{
                {\bfseries Deep and Structured Machine Learning}, 
                {\bfseries Digital Visual Effects},
                Design and Analysis of Algorithms, 
                Data Structure and Programming, 
                Probability and Statistics, 
                Linear Algebra
            }
        \end{cvskills}
    }
\end{cventries}
\vspace{-5mm}

\cvsection{Publications}
\cvsubsection{Conference Paper}
\begin{cvskills}{0.7cm}{15.7cm}
    \cvskill{[1]}{
        \link{http://stmharry.github.io/pdf/ECCV_2016.pdf}{Transfer Neural Trees for Heterogeneous Domain Adaptation.}
        Wei-Yu Chen, {\bfseries Tzu-Ming Harry Hsu}, Yao-Hung Hubert Tsai, and Yu-Chiang Frank Wang, in \emph{ECCV} 2016. 
    }
    \cvskill{[2]}{
        \link{http://stmharry.github.io/pdf/ICCV_2015.pdf}{Unsupervised Domain Adaptation With Imbalanced Cross-Domain Data.}
        {\bfseries Tzu-Ming Harry Hsu}, Wei-Yu Chen, Cheng-An Hou, Yao-Hung Hubert Tsai, Yi-Ren Yeh, and Yu-Chiang Frank Wang, in \emph{ICCV} 2015. 
    }
    \cvskill{[3]}{
        \link{http://stmharry.github.io/pdf/ICIP_2015.pdf}{Connecting the dots without clues: Unsupervised domain adaptation for cross-domain visual classification.}
        Wei-Yu Chen, {\bfseries Tzu-Ming Harry Hsu}, Cheng-An Hou, Yi-Ren Yeh and Yu-Chiang Frank Wang, in \emph{ICIP} 2015. 
    }
    \cvskill{[4]}{
        \link{http://stmharry.github.io/pdf/ICASSP_2015.pdf}{Robust Motion Artifact Reduction of Photoplethysmographic Signal with Trajectory Space Circular Model.}
        {\bfseries Tzu-Ming Harry Hsu}, Wei-Yu Chen, Kuan-Lin Chen, Mong-Chi Ko, You-Cheng Liu, An-Yeu Andy Wu, in \emph{ICASSP Signal Processing Cup} 2015. 
    }
\end{cvskills}

\cvsection{Honors \& Awards}
\cvsubsection{Group}
\begin{cvhonors}
    \cvhonor
    {Silver Medal Award}
    {Altera Innovate Asia FPGA Design Competition \ifelectronic\quad\link{http://stmharry.github.io/pdf/InnovateAsia_2015.pdf}{[Poster Link]}\fi \newline
    \tabitem Ranked \nth{2} among 20 teams with self-designed PCB integration}
    {Wu Han, China}
    {2015}
    \cvhonor
    {\nth{10} Place}
    {ICASSP Signal Processing Cup \ifelectronic\quad\link{http://stmharry.github.io/pdf/ICASSP_2015.pdf}{[PDF Link]}\fi \newline
    \tabitem Ranked \nth{10} globally in sports heartbeat detection with an error of 4.89 beats per minute (BPM)}
    {}
    {2015}
\end{cvhonors}

\cvsubsection{Individual}
\begin{cvhonors}
    \cvhonor
    {Presidential Award (5 times)}
    {Department of Electrical Engineering, NTU \newline
    \tabitem Awarded per semester to the top 5\% students}
    {}
    {2011 - 14}
    \cvhonor
    {World's \nth{1} Place and Gold Medal Award}
    {International Physics Olympiad (IPhO) \newline
    \tabitem Ranked \nth{1} in both theory section and experiment section among 500 national representatives from over 80 countries \ifelectronic\quad\link{https://en.wikipedia.org/wiki/International_Physics_Olympiad}{[Winner List]}\fi}
    {Bangkok, Thailand}
    {2011}
    \cvhonor
    {Gold Medal Award}
    {International Junior Science Olympiad (IJSO)}
    {Gyeong-Nam, South Korea}
    {2008}
\end{cvhonors}

\cvsection{Research Experiences}
\begin{cventries}
    \cventry
    {Intern student under the instruction of Dr. Yu-Chiang Frank Wang}
    {Multimedia and Machine Learning Lab}
    {CITI, Academia Sinica, Taiwan}
    {Apr. 2014 - Jun. 2016}
    {
        \begin{cvitems}
        \item{\bfseries Deep Learning for Feature Transformation}
            \begin{cvitems}
            \item{Build specific neural networks on target tasks to properly transform images to feature vectors, allowing recognition, neighbor querying, and possibly other tasks to be done.}
            \end{cvitems}
        \item{\bfseries Deep Learning for Heterogeneous Domain Adaptation}
            \begin{cvitems}
            \item{Transfer knowledge across different feature domains and build classifiers above the transferred knowledges}
            \item{An algorithm is proposed to transfer classifiers to a different dimensional space with deep neural network}
            \end{cvitems}
        \item{\bfseries Unsupervised Domain Adaptation with Imbalanced Cross-domain Data}
            \begin{cvitems}
            \item{Information of labeled source-domain data is transferred to the unlabeled target-domain, which may be a small set with imbalanced label counts}
            \item{An algorithm is proposed to combine sub-domain level classifiers to identify better source data applicability}
            \end{cvitems}
        \item{\bfseries Unsupervised Domain Adaptation with Balanced Cross-domain Data}
            \begin{cvitems}
            \item{A set of labeled source-domain data is used to construct classifier for the unlabeled target-domain data}
            \item{An algorithm is proposed to address source-target mismatch and project them to a common space}
            \end{cvitems}
        \item{\bfseries External Review}
            \begin{cvitems}
            \item{Review papers as external reviewer for \emph{IEEE ICCV}, \emph{IEEE ECCV}, \emph{IEEE AAAI}, and \emph{IEEE IJCAI}}
            \end{cvitems}
        \end{cvitems}
    }
    \cventry
    {Intern student under the instruction of Dr. An-Yeu Andy Wu}
    {Access IC Lab}
    {National Taiwan University}
    {Sep. 2014 - Jun. 2015}
    {
        \begin{cvitems}
        \item{\bfseries Noise Removal of Photoplethysmographic (PPG) Signals}
            \begin{cvitems}
            \item{Remove noises in PPG signals induced by motions by decorrelating the PPG with accelerometer signal}
            \item{An algorithm is proposed to project the signal into a complex plane, in which a temporal filter will be performed, followed by ensemble voting for the optimal beat counts}
            \end{cvitems}
        \end{cvitems}
    }
    \cventry
    {Intern student under the instruction of Dr. Jie-Hong Roland Jiang}
    {Laboratory for Applied Logic and Computation in System Design (ALCom Lab)}
    {National Taiwan University}
    {Jul. 2013 - Jun. 2014}
    {
        \begin{cvitems}
        \item{\bfseries Compressed Sensing}
            \begin{cvitems}
            \item{Compress the data perceived by a sensor array using less data storage than what it used to consume}
            \end{cvitems}
        \item{\bfseries Mathematical Neural models}
            \begin{cvitems}
            \item{Establish a time-continuous model of human neurons to simulate the biological effects at stimulus and message passing}
            \end{cvitems}
        \end{cvitems}
    }
\end{cventries}
\vspace{-5mm}

\cvsection{Work \& Teaching Experiences}
\begin{cventries}
    \cventry
    {Backend Engineer}
    {Digital Drift Corporation}
    {Taipei, Taiwan}
    {Mar. 2016 - Now}
    {
        \begin{cvitems}
        \item{\bfseries Deep Neural Networks for Image Interpretation}
            \begin{cvitems}
            \item{Build deep models for cuisine images using TensorFlow on multi-GPU machines, providing a backend with an API}
            \end{cvitems}
        \end{cvitems}
    }

    \cventry
    {Private Tutor}
    {Olympiad Tutoring Community}
    {Taipei, Taiwan}
    {Sep. 2011 - Jun. 2015}
    {
        \begin{cvitems}
        \item{Offer tutoring for high school physics, competition physics, GRE subject test (physics), and SAT II subject test (physics)}
        \item{Two students became national representatives for Taiwan in International Physics Olympiad (IPhO)}
        \end{cvitems}
    }
\end{cventries}

\iffalse
\cvsection{Selected Past Projects}
\begin{cvskills}{3.7cm}{12.5cm}
    \cvskill{Automatic Control}{A robust inverted pendulum-balancing bot that navigate along a track \ifelectronic\quad\link{https://www.youtube.com/watch?v=zKLleBYi6jc}{[YouTube Link]}\fi}
    \cvskill{Communication System}{A gesture-detecting system using Doppler effect on WiFi signal \ifelectronic\quad\link{https://www.youtube.com/watch?v=iwQ2nppWnd0}{[YouTube Link]}\fi}
    \cvskill{Embedded System}{{\bfseries EzBud}, a music manipulation platform that synchronizes with user heart rate during sporting}
    \cvskill{Speech Processing}{A complete system producing sentences from raw recordings using deep learning}
\end{cvskills}
\fi


\end{document}
