%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Author:
% Claud D. Park <posquit0.bj@gmail.com>
% http://www.posquit0.com
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Configuration
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Themes: Awesome-CV
\documentclass[12pt, a4paper]{awesome-cv}

%%% Override a directory location for fonts(default: 'fonts/')
\fontdir[fonts/]

%%% Configure a directory location for sections
\newcommand*{\sectiondir}{resume/}

%%% Override color
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight
%% Color for highlight
% Define your custom color if you don't like awesome colors
\colorlet{awesome}{awesome-red}
%\definecolor{awesome}{HTML}{CA63A8}
%% Colors for text
%\definecolor{darktext}{HTML}{414141}
%\definecolor{text}{HTML}{414141}
%\definecolor{graytext}{HTML}{414141}
%\definecolor{lighttext}{HTML}{414141}

%%% Override a separator for social informations in header(default: ' | ')
%\headersocialsep[\quad\textbar\quad]

\newif\ifelectronic
\electronicfalse

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     3rd party packages
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Needed to divide into several files
\usepackage{import}
\usepackage[super]{nth}
\usepackage{booktabs}
\usepackage{graphicx}
\newcommand{\tabitem}{~~\llap{\textbullet}~~}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Personal Data
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Essentials
\name{Tzu-Ming Harry}{Hsu}
\address{Department of Electrical Engineering and Computer Science, Massachusetts Institute of Technology}
\mobile{(+1) 617-803-7785} 
%%% Social
\email{stmharry@mit.edu}
\homepage{stmharry.github.io}
\github{stmharry}
%%% Optionals


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Content
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Make a footer for CV with three arguments(<left>, <center>, <right>)
\makecvfooter
{}
{Tzu-Ming Harry Hsu}
{\thepage}

\begin{document}

\makecvheader

\iffalse
\cvsection{Highlights}
\begin{cvskills}{0.7cm}{15.7cm}
    \cvskill{1}{\textbf{2} years in deep learning service deployment for Bite! APP with 40k users and 400k user images}
    \cvskill{2}{\textbf{2} majors acquired in undergraduate education: Electrical Engineering and Physics}
    \cvskill{3}{Ranked \textbf{\#1} in International Physics Olympiad 2011 in both theory and experiment among 400+ participants}
\end{cvskills}

\cvsection{Research Interests}
\begin{cvskills}{0.7cm}{15.7cm}
    \cvskill{1}{Deep Learning}
    \cvskill{2}{Computer Vision}
    \cvskill{3}{Machine Learning}
\end{cvskills}
\fi

\cvsection{Education}
\begin{cventries}
    \cventry
    {Ph.D. Student in Computer Science}
    {Massachusetts Institute of Technology (MIT)}
    {Cambridge, MA}
    {Sep. 2017 - Now}
    {}

    \cventry
    {B.S.E. in Electrical Engineering and B.S. in Physics}
    {National Taiwan University (NTU)}
    {Taipei, Taiwan}
    {Sep. 2011 - Jun. 2016}
    {
        \vspace{-3mm}
        \begin{cvskills}{2.7cm}{13.7cm}
            \cvskill{GPA}{Overall (3.99 / 4.00), Last 60 units (3.99 / 4.00)}
            \cvskill{Overall rank}{1 / 190}
            \iffalse
            \cvskill{Relevant courses}{
                {\bfseries Deep and Structured Machine Learning}, 
                {\bfseries Digital Visual Effects},
                Design and Analysis of Algorithms, 
                Data Structure and Programming, 
                Probability and Statistics, 
                Linear Algebra
            }
            \fi
        \end{cvskills}
    }
\end{cventries}
\vspace{-5mm}

\cvsection{Skills}
\begin{cvskills}{2.2cm}{14.2cm}
    \cvskill{Programming}{Python + TensorFlow, Docker, C / C++, MATLAB, Java, HTML / CSS / JS}
    \cvskill{Languages}{Mandarin Chinese (Native), Taiwanese (Native), English (Fluent), Spanish (Intermediate)}
    \iffalse
    \cvskill{Miscellaneous}{Beatbox, Mixology, Longboarding, Guitar}
    \fi
\end{cvskills}

\cvsection{Publications}
\cvsubsection{Conference Paper}
\begin{cvskills}{0.7cm}{15.7cm}
    \cvskill{[1]}{
        \link{https://arxiv.org/pdf/1808.09351}{3D-Aware Scene Manipulation via Inverse Graphics.}
        {\bfseries Tzu-Ming Harry Hsu*}, Shunyu Yao*, Jun-Yan Zhu, Jiajun Wu, Antonio Torralba, William T. Freeman, Joshua B. Tenenbaum, to be presented at \emph{NIPS} 2018
    }
    \cvskill{[2]}{
        \link{http://stmharry.github.io/pdf/ECCV_2016.pdf}{Transfer Neural Trees for Heterogeneous Domain Adaptation.}
        Wei-Yu Chen, {\bfseries Tzu-Ming Harry Hsu}, Yao-Hung Hubert Tsai, and Yu-Chiang Frank Wang, in \emph{ECCV} 2016. 
    }
    \cvskill{[3]}{
        \link{http://stmharry.github.io/pdf/ICCV_2015.pdf}{Unsupervised Domain Adaptation With Imbalanced Cross-Domain Data.}
        {\bfseries Tzu-Ming Harry Hsu}, Wei-Yu Chen, Cheng-An Hou, Yao-Hung Hubert Tsai, Yi-Ren Yeh, and Yu-Chiang Frank Wang, in \emph{ICCV} 2015. 
    }
    \cvskill{[4]}{
        \link{http://stmharry.github.io/pdf/ICIP_2015.pdf}{Connecting the dots without clues: Unsupervised domain adaptation for cross-domain visual classification.}
        Wei-Yu Chen, {\bfseries Tzu-Ming Harry Hsu}, Cheng-An Hou, Yi-Ren Yeh and Yu-Chiang Frank Wang, in \emph{ICIP} 2015. 
    }
    \cvskill{[5]}{
        \link{http://stmharry.github.io/pdf/ICASSP_2015.pdf}{Robust Motion Artifact Reduction of Photoplethysmographic Signal with Trajectory Space Circular Model.}
        {\bfseries Tzu-Ming Harry Hsu}, Wei-Yu Chen, Kuan-Lin Chen, Mong-Chi Ko, You-Cheng Liu, An-Yeu Andy Wu, in \emph{ICASSP Signal Processing Cup} 2015. 
    }
\end{cvskills}

\cvsection{Honors \& Awards}
\cvsubsection{Group}
\begin{cvhonors}
    \cvhonor
    {Silver Medal Award}
    {Altera Innovate Asia FPGA Design Competition \ifelectronic\quad\link{http://stmharry.github.io/pdf/InnovateAsia_2015.pdf}{[Poster Link]}\fi \newline
    \tabitem Ranked \nth{2} among 20 teams with self-designed PCB integration}
    {Wu Han, China}
    {2015}
    \cvhonor
    {\nth{10} Place}
    {ICASSP Signal Processing Cup \ifelectronic\quad\link{http://stmharry.github.io/pdf/ICASSP_2015.pdf}{[PDF Link]}\fi \newline
    \tabitem Ranked \nth{10} globally in sports heartbeat detection with an error of 4.89 beats per minute (BPM)}
    {}
    {2015}
\end{cvhonors}

\cvsubsection{Individual}
\begin{cvhonors}
    \cvhonor
    {Presidential Award (5 times)}
    {Department of Electrical Engineering, NTU \newline
    \tabitem Awarded per semester to the top 5\% students}
    {}
    {2011 - 14}
    \cvhonor
    {World's \nth{1} Place and Gold Medal Award}
    {International Physics Olympiad (IPhO) \newline
    \tabitem Ranked \nth{1} in both theory section and experiment section among 500 national representatives from over 80 countries \ifelectronic\quad\link{https://en.wikipedia.org/wiki/International_Physics_Olympiad}{[Winner List]}\fi}
    {Bangkok, Thailand}
    {2011}
    \cvhonor
    {Gold Medal Award}
    {International Junior Science Olympiad (IJSO)}
    {South Korea}
    {2008}
\end{cvhonors}

\newpage

\cvsection{Research Experiences}
\begin{cventries}
    \cventry
    {Ph.D. Student of Prof. Peter Szolovits}
    {Clinical Descision Making Group}
    {CSAIL, MIT}
    {Jul. 2018 - Now}
    {
        \begin{cvitems}
        \item{\bfseries Unsupervised Machine Learning for Healthcare}
            \begin{cvitems}
                \item{Align clinical imaging data and radiology reports with representation learning.}
            \end{cvitems}
        \end{cvitems} 
    }
    \vspace{-5mm}

    \cventry
    {}
    {Computer Vision Group}
    {CSAIL MIT}
    {Feb. 2018 - Now}
    {
        \begin{cvitems}
        \item{\bfseries 3D Inverse-Graphics}
            \begin{cvitems}
                \item{Develop vision as inverse-graphics for 3D scene understanding.}
            \end{cvitems}
        \end{cvitems} 
    }
    \vspace{-5mm}

    \cventry
    {Research Assistant of Dr. Fadel Adib}
    {Signal Kinetics Lab}
    {Media Lab, MIT}
    {Sep. 2017 - Jan. 2018}
    {
        \begin{cvitems}
        \item{\bfseries Agent Co-localization via Cellular Network}
            \begin{cvitems}
                \item{Construct Bayesian model based on LTE channel estimation and locate agents in an area simultaneously.}
            \end{cvitems}
        \end{cvitems} 
    }
    \vspace{-5mm}

    \cventry
    {Intern student under the instruction of Dr. Yu-Chiang Frank Wang}
    {Multimedia and Machine Learning Lab}
    {CITI, Academia Sinica, Taiwan}
    {Apr. 2014 - Jun. 2016}
    {
        \begin{cvitems}
        \item{\bfseries Deep Learning for Feature Transformation}
            \begin{cvitems}
            \item{Build specific neural networks on target tasks to properly transform images to feature vectors, allowing recognition, neighbor querying, and possibly other tasks to be done.}
            \end{cvitems}
        \item{\bfseries Deep Learning for Heterogeneous Domain Adaptation}
            \begin{cvitems}
            \item{Transfer knowledge across different feature domains and build classifiers above the transferred knowledges}
            \item{An algorithm is proposed to transfer classifiers to a different dimensional space with deep neural network}
            \end{cvitems}
        \item{\bfseries Unsupervised Domain Adaptation with Imbalanced Cross-domain Data}
            \begin{cvitems}
            \item{Information of labeled source-domain data is transferred to the unlabeled target-domain, which may be with imbalanced labels}
            \item{An algorithm is proposed to combine sub-domain level classifiers to identify better source data applicability}
            \end{cvitems}
        \item{\bfseries Unsupervised Domain Adaptation with Balanced Cross-domain Data}
            \begin{cvitems}
            \item{A set of labeled source-domain data is used to construct classifier for the unlabeled target-domain data}
            \item{An algorithm is proposed to address source-target mismatch and project them to a common space}
            \end{cvitems}
        \item{\bfseries External Review}
            \begin{cvitems}
            \item{Review papers as external reviewer for \emph{ICCV}, \emph{ECCV}, \emph{AAAI}, and \emph{IJCAI}}
            \end{cvitems}
        \end{cvitems}
    }
    \vspace{-5mm}

    \cventry
    {Intern student under the instruction of Dr. An-Yeu Andy Wu}
    {Access IC Lab}
    {National Taiwan University}
    {Sep. 2014 - Jun. 2015}
    {
        \begin{cvitems}
        \item{\bfseries Noise Removal of Photoplethysmographic (PPG) Signals}
            \begin{cvitems}
            \item{Remove noises in PPG signals induced by motions by decorrelating the PPG with accelerometer signal}
            \item{An algorithm is proposed to project the signal into a complex plane, in which a temporal filter will be performed, followed by ensemble voting for the optimal beat counts}
            \end{cvitems}
        \end{cvitems}
    }
    \vspace{-5mm}

    \cventry
    {Intern student under the instruction of Dr. Jie-Hong Roland Jiang}
    {Laboratory for Applied Logic and Computation in System Design (ALCom Lab)}
    {National Taiwan University}
    {Jul. 2013 - Jun. 2014}
    {
        \begin{cvitems}
        \item{\bfseries Compressed Sensing}
            \begin{cvitems}
            \item{Compress the data perceived by a sensor array using less data storage than what it used to consume}
            \end{cvitems}
        \item{\bfseries Mathematical Neural models}
            \begin{cvitems}
            \item{Establish a time-continuous model of human neurons to simulate the biological effects at stimulus and message passing}
            \end{cvitems}
        \end{cvitems}
    }
\end{cventries}
\vspace{-5mm}

\cvsection{Work \& Teaching Experiences}
\begin{cventries}
    \cventry
    {Backend Engineer}
    {Digital Drift Corporation}
    {Taipei, Taiwan}
    {Mar. 2016 - Aug. 2017}
    {
        \begin{cvitems}
        \item{\bfseries Deep Neural Networks for Image Interpretation}
            \begin{cvitems}
            \item{Build deep models for cuisine images using TensorFlow on multi-GPU machines, providing a backend with an API}
            \end{cvitems}
        \end{cvitems}
    }

    \iffalse
    \cventry
    {Private Tutor}
    {Olympiad Tutoring Community}
    {Taipei, Taiwan}
    {Sep. 2011 - Jun. 2015}
    {
        \begin{cvitems}
        \item{Offer tutoring for high school physics, competition physics, GRE subject test (physics), and SAT II subject test (physics)}
        \item{Two students became national representatives for Taiwan in International Physics Olympiad (IPhO)}
        \end{cvitems}
    }
    \fi
\end{cventries}

\end{document}
